---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# webgem

<!-- badges: start -->
<!-- badges: end -->

The goal of webgem is to make baseball hitting metrics easier to interpret by ranking, scaling, and visualizing player statistics.

## Installation

You can install the development version of webgem from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
# install.packages("devtools")
devtools::install_github("connerrob24/webgem")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(webgem)
```

#### metricRank Example

```{r}
metricRank(
  x = webgem_data$ops,
  threshold = 0.8,
  lower_label = "mediocre ops",
  upper_label = "great ops"
)
```

#### hitterProfile Example

```{r}
player_data <- webgem_data[webgem_data$player == "Shohei Ohtani", ]

ohtani_profile <- hitterProfile(
  player = player_data$player,
  wrc_plus = player_data$wrc_plus,
  ops = player_data$ops,
  obp = player_data$obp,
  slg = player_data$slg,
  avg = player_data$avg,
  iso = player_data$iso,
  war = player_data$war,
  woba = player_data$woba,
  bb_pct = player_data$bb_pct,
  barrel_pct = player_data$barrel_pct,
  hard_hit_pct = player_data$hard_hit_pct
)

ohtani_profile
```

#### hitterRadar Example

```{r}
hitterRadar(ohtani_profile)
```

