---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# webgem

<!-- badges: start -->
<!-- badges: end -->

`webgem` is an R package for ranking, scaling, and visualizing baseball hitting metrics. The package is designed to make offensive statistics easier to interpret by turning raw numeric values into clear labels, scaled hitter profiles, and radar plots. With that, the goal of `webgem` is to provide users with a streamlined process at interpreting metrics through ranking, scaling, and visualizing player statistics.

## Installation

You can install the development version of webgem from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
# install.packages("devtools")
devtools::install_github("ADC-405-S26/webgem")
```

## Main Functions

The package includes three main functions:

- `metricRank()` labels numeric values using one or two user-defined thresholds.
- `hitterProfile()` creates a scaled hitter profile from selected offensive metrics.
- `hitterRadar()` creates a radar plot from a hitter profile.


## `Examples`

```{r example}
library(webgem)
```

## `metricRank` Example

*one threshold*
```{r}
metricRank(
  x = webgem_data$ops,
  threshold = 0.8,
  lower_label = "mediocre ops",
  upper_label = "great ops"
)
```

*two thresholds*
```{r}
metricRank(
  x = webgem_data$ops,
  threshold = 0.7,
  upper_threshold = 0.9,
  lower_label = "bad ops",
  middle_label = "okay ops",
  upper_label = "great ops"
)
```

## `hitterProfile` Example

```{r}
player_data <- webgem_data[webgem_data$player == "Shohei Ohtani", ]

ohtani_profile <- hitterProfile(
  player = player_data$player,
  wrc_plus = player_data$wrc_plus,
  ops = player_data$ops,
  obp = player_data$obp,
  slg = player_data$slg,
  avg = player_data$avg,
  iso = player_data$iso,
  war = player_data$war,
  woba = player_data$woba,
  bb_pct = player_data$bb_pct,
  barrel_pct = player_data$barrel_pct,
  hard_hit_pct = player_data$hard_hit_pct
)

ohtani_profile
```

## hitterRadar Example

```{r}
hitterRadar(ohtani_profile)
```

